Effectiveness of community-based TURF-reserves in small-scale fisheries

### 2018-12-04 docs/paper/Villasenor-Derbez.Rmd
Added a brief text that will close #31
Clarified that fishing occurs only outside the reserves to close #34

We evaluate three TURF-reserves in Mexico (Fig \ref{fig:map}A). The first one was created by the *Buzos y Pescadores de la Baja California* fishing cooperative, located in Isla Natividad in the Baja California Peninsula (Fig \ref{fig:map}B). The main fishery in the island is the spiny lobster (*Panulirus interruptus*), but other resources like finfish, sea cucumber, read sea urchin, snail, and abalone are also an important source of income. In 2006, the community decided to implement two marine reserves within their fishing grounds to protect commercially important invertebrate species; mainly lobster and abalone. While these reserves obtained legal recognition only in 2018 \citep{dof_website_2018}, they have been well enforced since their implementation.

@@

The fact that these reserves were re-established and just enacted shows a comitment of support (issue \#16 on GH).

>>>>

We evaluate three community-based no-take marine reserves implemented in Mexican TURF-managed fisheries, therefore making them TURF-reserves (Fig \ref{fig:map}A). The first one was created by the *Buzos y Pescadores de la Baja California* fishing cooperative, located in Isla Natividad in the Baja California Peninsula (Fig \ref{fig:map}B). The main fishery in the island is the spiny lobster (*Panulirus interruptus*), but other resources like finfish, sea cucumber, read sea urchin, snail, and abalone are also an important source of income. In 2006, the community decided to implement two marine reserves within their fishing grounds to protect commercially important invertebrate species; mainly lobster and abalone. While these reserves obtained legal recognition only in 2018 \citep{dof_website_2018}, they have been well enforced since their implementation.

@@

The fact that these reserves were re-established and just enacted shows a comitment of support (issue \#16 on GH). the SES provides a static picture of governance and resource conditions, whereas the biological assessment reflects changes through time (Isse \#31).
